sentiment-analysis

### 2016-08-03 eda/sentiment-analysis.Rmd
rscripts for cleaning

Now to apply this sentiment analysis to the Yelp review dataset, I have to mutate the data so that each word for every review exists in one row. I also need to remove stop words like "the", "and", "I", etc. since they don't indicate anything about the attitude of the reviewer and shouldn't affect the valence score. A library called __tm__ for text mining can eliminate stop words. 
```{r, eval = F}
review_words <- reviews %>% 
  mutate(words = str_split(text, "[ ,.]")) %>% 
  unnest(words)

@@

>>>>

Now to apply this sentiment analysis to the Yelp review dataset, I have to mutate the data so that each word for every review exists in one row. I also need to remove stop words like "the", "and", "I", etc. since they don't indicate anything about the attitude of the reviewer and shouldn't affect the valence score. A library called __tm__ for text mining can eliminate stop words.
I'll read in the first 500,000 observations of the Yelp reviewers data, which has been written to a csv file.
```{r, eval = F}
reviews <- read_csv("clean_data/reviews.csv")

review_words <- reviews %>% 
  mutate(words = str_split(text, "[ ,.]")) %>% 
  unnest(words)

@@

Positive correlation exists! Some inaccuracy (outliers on boxplots). Find out most common positive and negative words in reviews, creating a summary of the counts.

```{r}
review_words <- reviews_text %>% 
  count(review_id, business_id, stars, word) %>% 
  ungroup() %>% 
  group_by(business = n_distinct(business_id),
           reviews = n(),
           use = sum(n),
           average_star = mean(stars)) %>% 
  ungroup()
```
